---
title: \advance\leftskip-3cm\includegraphics{Slide_Cover.pdf}
author: ""
date: ""
output: 
  beamer_presentation:
    latex_engine: xelatex
    fig_crop: no
    fonttheme: professionalfonts
    template: default-beamer-twocol.tex
    toc: yes
fontsize: 8pt
mainfont: Calibri
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dev = 'pdf')
# Load libraries and data
library(survey)
library(RColorBrewer)

#Data - Vietnam Era  Veterans Survey Design Object
viet_design <- readRDS("Data_Viet_Design.Rds")

#Data - Age Over 55 General Population Survey Design Object
per55_design <- readRDS("Data_Per55_Design.Rds")

#Data - Housing Vietnam Vets
hou_viet_design <- readRDS("Data_Hou_Viet_Design.Rds")

#Data - Housing Age Over 55 General Population
hou55_design <- readRDS("Data_Hou55_Design.Rds")

#Data - Vietnam Era Veterans GQ Survey  Desgn Object
viet_gq_design <- readRDS("Data_Per_Viet_GQ_Design.Rds")

#Data - General Populaiton GQ Survey  Desgn Object
per55_gq_design <- readRDS("Data_Per55_GQ_Design.Rds")

#Data - Utilization data for Vietnam Vets
uvr15 <- read.csv("UVR_2015_161212_VietVet.csv", sep=",", stringsAsFactors=FALSE)

#Graph stuff
#create var to reset graphical parameters
opar <-par(no.readonly=TRUE)

#Paired color vector to comparisons 
mycols <- brewer.pal(n=12, name = "Paired")

```

```{r age_setup, include=FALSE}
#calculate vietnam vet total (counts)
viet.total <- svytotal(~Period, viet_design)
#calculate median age for vietnam vets
agep.v.qt <- svyquantile(~AGEP, viet_design, quantiles = c(0.5))
#calculate median age for General Population
agep.gp.qt <- svyquantile(~AGEP, per55_design, quantiles = c(0.5))

#calculate age means (percentage) for vietnam vets, extract std errors
age.v <- svymean(~Ager, viet_design)
age.se.v <- SE(age.v)[6:10]
age.v <- age.v[6:10]
#calculate age means (percentage) for General Population, extract std errors
age.gp <- svymean(~Ager, per55_design)
age.se.gp <- SE(age.gp)[6:10]
age.gp <- age.gp[6:10]

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
age.z <- c() 
for(i in 1:length(age.v)){
  zscore<- (age.v[i]-age.gp[i])/sqrt(age.se.v[i]^2+age.se.gp[i]^2)
  age.z <- c(zscore, age.z)
  if(all(age.z > 1.96 | age.z < -1.96)==TRUE) age.zscore <- "Differences are significant at the 95% confidence level" else age.zscore <- "Differences are not significant."
}

#multiply by 100 to get percentages
age.v <- age.v*100
age.gp <- age.gp*100

```

```{r sex_setup, include=FALSE}
#calculate sex means (percentage) for vietnam vets, extract std errors
sex.v <- svymean(~SEX, viet_design)
sex.se.v <- SE(sex.v)
#calculate sex means (percentage) for General Population, extract std errors
sex.gp <- svymean(~SEX, per55_design)
sex.se.gp <- SE(sex.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
sex.z <- c() 
for(i in 1:length(sex.v)){
  zscore<- (sex.v[i]-sex.gp[i])/sqrt(sex.se.v[i]^2+sex.se.gp[i]^2)
  sex.z <- c(zscore, sex.z)
  if(all(sex.z > 1.96 | sex.z < -1.96)==TRUE) sex.zscore <- "Differences are significant at the 95% confidence level" else sex.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
sex.v <- sex.v*100
sex.gp <- sex.gp*100

#calculate GP totals by sex (used in slide header)
sex.gp.tot <- (svytotal(~SEX, per55_design))/1000000
```

# Data Sources and Issues

## Data Sources: American Community Survey (ACS) and Unique Veteran Report (UVR)

* The primary data source is the [\textcolor{blue}{2015 ACS Public Use Microdata Sample (PUMS)}](https://www.census.gov/programs-surveys/acs/data/pums.html). The UVR is also used to provide a view into utilization of VA services. 
    * The ACS is an ongoing survey that provides annual data on the social and economic characteristics of the U.S. population.
    * The ACS uses a series of monthly samples to produce annually updated data for the same small areas (census tracts and block groups)formerly surveyed via the decennial census long-form sample.
    * The UVR is internal report created for VA leadership to answer basic questions on the utilization of VA services by Veterans.

* All comparative statements (Vietnam Veterans vs. General Population) have undergone statistical testing according to the [\textcolor{blue}{method prescribed in the ACS technical documentation}](https://www2.census.gov/programs-surveys/acs/tech_docs/statistical_testing/2015StatisticalTesting1year.pdf). Results are significant at the 95% confidence level.
    * A “statistically significant difference” simply means there is statistical evidence that there is a difference; it does not mean the difference is necessarily large, important or significant in the usual sense of the word.’
    * A “no statistically significant difference” means that there is statistical evidence that there is no difference in the comparative percentages/rates.
    
* Race categories are shown for the non-Hispanic population (e.g., White non-Hispanic, Black non-Hispanic, Asian non-Hispanic). Hispanics can be of any race.
    * The Native Hawaiians and Pacific Islanders category is abbreviated as "NHOPI". They are also grouped together with the "Asian" category.
    * “Other” includes individuals who reported as belonging to "Some Other Race" or " Two or More Races".
    * American Indians and Alaska Natives are grouped together and are abbreviated as "AIAN"
    
* For more information about the ACS please visit the [\textcolor{blue}{U.S. Census Bureau webiste}](http://www.census.gov/acs).


## Issues to Consider When Comparing Vietnam Veteran to Non-Veterans

* Between 1964 and 1973, there were roughly 8.8 million[^1] personnel, composed of both volunteers and draftees, who served in the Vietnam War. As of 2015 there are an estimated `r round(viet.total[[5]]/1000000, digits=1)`M Veterans. 

* Estimates reported here do not represent the number of troops deployed, killed, or wounded. They only represent Veterans who responded to the ACS in 2015. 

* Vietnam Veterans are predominantly men (`r round(sex.v[1], digits=0)`%) whereas non-Veterans are mostly women (`r round(sex.gp[2], digits=0)`%). Any characteristic associated with sex will be affected by the inherent differences amongst men and women. 

* Vietnam Veterans are compared with non-Veterans (General Population) of the same age group i.e. `r min(viet_design$variables$AGEP)` years and older. 

* A bulk of Vietnam War Veterans (`r round(max(age.v), digits=0)`%) are  between 65 and 74 years old. Whereas `r round(max(age.gp), digits=0)`% of the General Population are between 55 an 64 years old. Veteran median age is around `r agep.v.qt[[1]]` compared with `r agep.gp.qt[[1]]` for non-Veterans.

* Between December 1969 and March 1975, there were seven[^2] draft lottery drawings inducting roughly 75,717 registrants born between 1944 and 1956.

* There are issues of selection bias in any comparison of Veterans and non-Veterans. Volunteers choose to enlist and are then chosen by the military based on specific criteria, both mental and physical, that may set them apart from the population who chose not to enlist. Any effects ascribed to military service may be attributable to pre-service characteristics and not necessarily Veteran status.
    
[^1]:[U.S. Department of Commerce, Bureau of the Census, "Vietnam Conflict—U.S. Military Forces in Vietnam and Casualties Incurred: 1961 to 1972," table 590, Statistical Abstract of the United States, 1977 (Washington, D.C.: U.S. Department of Commerce, Bureau of the Census, 1980), 369.](https://www2.census.gov/library/publications/1977/compendia/statab/98ed/1977-05.pdf)

[^2]:[Selective Service System, "The Vietnam Lotteries"](https://www.sss.gov/About/History-And-Records/lotter1)


# Demographic Characteristics

## Estimated `r round(viet.total[[5]]/1000000, digits=1)`M Veterans from the Vietnam War Era. Ages range from `r max(viet_design$variables$AGEP)` to `r min(viet_design$variables$AGEP)` years old (born between `r 2015-max(viet_design$variables$AGEP)` and `r 2015-min(viet_design$variables$AGEP)`). Median age is `r agep.v.qt[[1]]` years. 

<!-- age_setup at the top as it used in intro slide -->
  \columnsbegin
\column{.5\textwidth}
```{r age_hist, out.width='2.0in'}
#set graphical parameters
par(mar=c(5,4,4,2),  cex.axis=1, cex.lab=1, col.lab="gray60", col.axis="gray60")

#histogramalama!
svyhist(~AGEP, 
        viet_design,
        breaks = 55:100,
        freq = TRUE,
        border="#ffffff",
        col="#b2df8a", 
        lwd=0.4,
        las=1,
        main="",
        xlab=NA,
        ylab=NA, 
        ylim=c(0, 700000),
        axes = FALSE)

#custom y- axis
axis(side=2, at=seq(0, 700000, 100000), labels=seq(0, 700, 100), las=1,  pos=55,lwd=0, lwd.tick=0.15, col.ticks="gray60", tick=TRUE, tck=-0.01)
#custom y- axis Label
title(ylab="Number of Veterans (in 000s)", line = 1.5)
#custom x axis
axis(side=1, at=seq(55, 100, 5), labels=TRUE, pos=0, lwd=0, lwd.tick=0.15, col.ticks="gray60", tick=TRUE, tck=-0.01)
#custom x- axis Label
title(xlab="Age", line = 1.5)

#draw Median as reference line
abline(v = agep.v.qt, col = "red")
text(x=agep.v.qt+0.25, y=690000, srt=270, "Median", adj=c(0.5, -0.1), cex=0.8, col="gray10")

#reset graph parameters
par(opar)

```

```{r age_v_bar, out.width='2.0in'}

#set graphical parameters and colors
par(mar=c(5,6,0,2), cex=1.75,  col.axis="gray60")

#barplot of AGE for VIETNAM VETS
midpoints <- barplot(height=age.v,
                     names.arg=c("55 - 64", "65 - 74", "75 - 84", "85 - 94", "95 - 99"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=age.v+8, y=midpoints, labels=paste(round(age.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```
\column{.5\textwidth}
```{r age_gp_hist, out.width='2.0in'}
#set graphical parameters
par(mar=c(5,4,4,2),  cex.axis=1, cex.lab=1, col.lab="gray60", col.axis="gray60")

#histogramalama!
svyhist(~AGEP, 
        per55_design,
        breaks = 55:100,
        freq = TRUE,
        border="#ffffff",
        col="#33a02c", 
        lwd=0.4,
        las=1,
        main="",
        xlab=NA,
        ylab=NA, 
        ylim=c(0, 9000000),
        axes = FALSE)

#custom y- axis
axis(side=2, at=seq(0, 9000000, 1000000), labels=seq(0, 9, 1), las=1,  pos=55,lwd=0, lwd.tick=0.15, col.ticks="gray60", tick=TRUE, tck=-0.01)
#custom y- axis Label
title(ylab="Number of Veterans (in Millions)", line = 1.5)
#custom x axis
axis(side=1, at=seq(55, 100, 5), labels=TRUE, pos=0, lwd=0, lwd.tick=0.15, col.ticks="gray60", tick=TRUE, tck=-0.01)
#custom x- axis Label
title(xlab="Age", line = 1.5)

#draw Median as reference line
abline(v = agep.gp.qt, col = "red")
text(x=agep.gp.qt+0.25, y=8400000, srt=270, "Median", adj=c(0.5, -0.1), cex=0.8, col="gray10")

#reset graph parameters
par(opar)

```

```{r age_gp_bar, out.width='2.0in'}
#set graphical parameters and colors
par(mar=c(5,6,0,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of AGE for GENERAL POPULATION
midpoints <- barplot(height=age.gp,
                     names.arg=c("55 - 64", "65 - 74", "75 - 84", "85 - 94", "95 - 99"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=age.gp+8, y=midpoints, labels=paste(round(age.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)


```
\columnsend
\tinyrfont
_`r age.zscore`_

## An overwhelming majority of Vietnam War Veterans are male (`r round((viet.total[[5]]*sex.v[[1]])/100000000, digits=1)`M) while in the General Population females (`r round(sex.gp.tot[[2]], digits=1)`M) outnumber males by `r round(sex.gp.tot[[2]]-sex.gp.tot[[1]], digits=1)`M. 

<!-- sex_setup at the top as it used in intro slide -->
\columnsbegin
\column{.5\textwidth}
```{r sex_v_bar, out.width='2in'}
#set graphical parameters
par(mar=c(5,4,4,2), cex=2, col.lab="gray16", col.axis="gray30")

#barplot of Vietnam Vets by Sex
midpoints <- barplot(height=sex.v,
                     space=0.5,
                     names.arg=c("M","F"),
                     horiz=TRUE,
                     col=mycols[c(10,12)],
                     border=NA,
                     xlim=c(0,110),
                     axes=FALSE
)

#x-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=sex.v, y=midpoints, labels=paste(round(sex.v, digits=1), "%"), col="gray16", pos=4)
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{.5\textwidth}
```{r sex_gp_bar, out.width='2in'}
#set graphical parameters
par(mar=c(5,4,4,2), cex=2, col.lab="gray16", col.axis="gray30")

#barplot of General Population (Age >55) by Sex
midpoints <- barplot(height=sex.gp,
                     space=0.5,
                     names.arg=c("M", "F"),
                     horiz=T,
                     col=mycols[c(9, 11)],
                     border=NA,
                     xlim=c(0,110),
                     axes=FALSE
)

#x-axis label
mtext("Percentage of General Population", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=sex.gp, y=midpoints, labels=paste(round(sex.gp, digits=1), "%"), col="gray16", pos=4)
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r sex.zscore`_

## Non-Hispanic Whites are the largest racial group amongst Vietnam War Veterans and General Population.

```{r race_setup}
#calculate racenhc means (percentage) for vietnam vets, extract std errors
racenhc.v <- svymean(~RaceNHC, viet_design)
racenhc.se.v <- SE(racenhc.v)
#calculate racenhc means (percentage) for General Population, extract std errors
racenhc.gp <- svymean(~RaceNHC, per55_design)
racenhc.se.gp <- SE(racenhc.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
racenhc.z <- c() 
for(i in 1:length(racenhc.v)){
  zscore<- (racenhc.v[i]-racenhc.gp[i])/sqrt(racenhc.se.v[i]^2+racenhc.se.gp[i]^2)
  racenhc.z <- c(zscore, racenhc.z)
  if(all(racenhc.z > 1.96 | racenhc.z < -1.96)==TRUE) racenhc.zscore <- "Differences are significant at the 95% confidence level" else racenhc.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
racenhc.v <- racenhc.v*100
racenhc.gp <- racenhc.gp*100

```

\columnsbegin
\column{.5\textwidth}
```{r race_v_bar, out.width='2in'}

#set graphical parameters and colors
par(mar=c(5,7,1,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of AGE for VIETNAM VETS
midpoints <- barplot(height=racenhc.v,
                     names.arg=c("American Indian\nAlaska Native", "Asian/NHOPI", "Black", "Hispanic", "Other", "White"),
                     horiz=TRUE,
                     col=mycols[seq(1,12,2)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=racenhc.v+8, y=midpoints, labels=paste(round(racenhc.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```
\column{.5\textwidth}
```{r race_gp_bar, out.width='2in'}

#set graphical parameters and colors
par(mar=c(5,7,1,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of AGE for VIETNAM VETS
midpoints <- barplot(height=racenhc.gp,
                     names.arg=c("American Indian\nAlaska Native", "Asian/NHOPI", "Black", "Hispanic", "Other", "White"),
                     horiz=TRUE,
                     col=mycols[seq(0,12,2)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=racenhc.gp+8, y=midpoints, labels=paste(round(racenhc.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r racenhc.zscore`_

## Relative to the General Population, Vietnam Veterans are more likely to be married and less likely to be widowed. 

```{r marital_setup}
#calculate mar means (percentage) for vietnam vets, extract std errors
mar.v <- svymean(~MAR, viet_design)
mar.se.v <- SE(mar.v)
#calculate mar means (percentage) for General Population, extract std errors
mar.gp <- svymean(~MAR, per55_design)
mar.se.gp <- SE(mar.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
mar.z <- c() 
for(i in 1:length(mar.v)){
  zscore<- (mar.v[i]-mar.gp[i])/sqrt(mar.se.v[i]^2+mar.se.gp[i]^2)
  mar.z <- c(zscore, mar.z)
  if(all(mar.z > 1.96 | mar.z < -1.96)==TRUE) mar.zscore <- "Differences are significant at the 95% confidence level" else mar.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
mar.v <- mar.v*100
mar.gp <- mar.gp*100
```
\columnsbegin
\column{0.5\textwidth}
```{r marital_v_bar, out.width='2.25in'}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of MARITAL STATUS for VIETNAM VETS
midpoints <- barplot(height=mar.v,
                     names.arg=c("Married", "Widowed", "Divorced", "Separated", "Never\nMarried"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7,9)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.75, col="gray60")
#custom labels 
text(x=mar.v+8, y=midpoints, labels=paste(round(mar.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)


```
\column{0.5\textwidth}
```{r marital_gp_bar, out.width='2.25in'}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of MARITAL STATUS for GENERAL POPULATION
midpoints <- barplot(height=mar.gp,
                     names.arg=c("Married", "Widowed", "Divorced", "Separated", "Never\nMarried"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8,10)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.75)
#custom labels 
text(x=mar.gp+8, y=midpoints, labels=paste(round(mar.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)


```
\columnsend
\tinyrfont
_`r mar.zscore`_
\normalfont
Note: Vietnam War Veterans are mostly male and women have a higher life expectancy (need source.)

## Veterans are marginally more likely to be disabled though their disability is not necessarily service connected. About a third of disabled Veterans are more than 70% disabled. 

```{r dis_setup}

#Disability Recode (DIS) VIETNAM VETERANS extract std errors
dis.v <- svymean(~DIS, viet_design)
dis.se.v <- SE(dis.v)
#Disability Recode (DIS) GENERAL POPULATION, extract std errors
dis.gp <- svymean(~DIS, per55_design)
dis.se.gp <- SE(dis.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
dis.z <- c() 
for(i in 1:length(dis.v)){
  zscore<- (dis.v[i]-dis.gp[i])/sqrt(dis.se.v[i]^2+dis.se.gp[i]^2)
  dis.z <- c(zscore, dis.z)
  if(all(dis.z > 1.96 | dis.z < -1.96)==TRUE) dis.zscore <- "Disability status differences are significant at the 95% confidence level" else dis.zscore <- "Disability status differences are not significant."
}
#multiply by 100 to get percentages
dis.v <- dis.v*100
dis.gp <- dis.gp*100

```

```{r dratx_setup}

## Veterans Service Connected Disability Rating (DRATX)
dratx.v <- svymean(~DRATX, viet_design)*100

## Veteran Service Connected Disability STATUS (DRAT)
drat.v <- svymean(~DRAT, viet_design, na.rm = TRUE)*100

# No sig test since these variables are not compared with the General Population

```

\columnsbegin
\column{.5\textwidth}
```{r dis_v_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of DISABILITY STATUS for VIETNAM VETS
midpoints <- barplot(height=dis.v,
                     space=0.5,
                     names.arg=c("With", "Without"),
                     horiz=TRUE,
                     col=mycols[c(1,3)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=3
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#custom labels 
text(x=dis.v+8, y=midpoints, labels=paste(round(dis.v, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("Disability Status", side=2, adj=0.5, line=2.75, las=0, cex=1.5, col="gray60")

#reset graph parameters
par(opar)

```

```{r dis_gp_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of DISABILITY STATUS for GENERAL POP
midpoints <- barplot(height=dis.gp,
                     space=0.5,
                     names.arg=c("With", "Without"),
                     horiz=TRUE,
                     col=mycols[c(2,4)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=3
)


#X-axis label
mtext("Percentage of General Population", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#custom labels 
text(x=dis.gp+8, y=midpoints, labels=paste(round(dis.gp, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("Disability Status", side=2, adj=0.5, line=2.75, las=0, cex=1.5, col="gray60")

#reset graph parameters
par(opar)

```
\column{.5\textwidth}
```{r dratx_v_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,5,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Service Connected Disability for VIETNAM VETS
midpoints <- barplot(height=dratx.v,
                     space=0.5,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(9,11)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)
#custom labels 
text(x=dratx.v+8, y=midpoints, labels=paste(round(dratx.v, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("Service Connected Disability (SCD)", side=2, adj=0.5, line=2.9, las=0, cex=1.5, col="gray60")

#reset graph parameters
par(opar)

```

```{r drat_v_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of DISABILITY RATING for VIETNAM VETS
midpoints <- barplot(height=drat.v,
                     names.arg=c("0%", "10-20%", "30-40%", "50-60%", "70%<", "Not\nReported"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7,9,11)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)
#custom labels 
text(x=drat.v+8, y=midpoints, labels=paste(round(drat.v, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("SCD Rating", side=2, adj=0.5, line=5, las=0, cex=1.5, col="gray60")

#reset graph parameters
par(opar)


```
\columnsend

\tinyrfont
_`r dis.zscore`_

## Independent Living Difficulty

```{r dout_setup}

#Independent Living Difficulty (DOUT) VIETNAM VETS,  extract std errors
dout.v <- svymean(~DIS, viet_design)
dout.se.v <- SE(dout.v)
#Independent Living Difficulty (DOUT) GENERAL POPULATION, extract std errors
dout.gp <- svymean(~DIS, per55_design)
dout.se.gp <- SE(dout.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
dout.z <- c() 
for(i in 1:length(dout.v)){
  zscore<- (dout.v[i]-dout.gp[i])/sqrt(dout.se.v[i]^2+dout.se.gp[i]^2)
  dout.z <- c(zscore, dout.z)
  if(all(dout.z > 1.96 | dout.z < -1.96)==TRUE) dout.zscore <- "Differences are significant at the 95% confidence level" else dout.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
dout.v <- dout.v*100
dout.gp <- dout.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r dout_v_bar, out.width='2.0in'}

#set graphical parameters and colors
par(mar=c(5,4,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of DISABILITY RATING for VIETNAM VETS
midpoints <- barplot(height=dout.v,
                     space=0.5,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(9,11)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=dout.v+8, y=midpoints, labels=paste(round(dout.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{0.5\textwidth}
```{r dout_gp_bar, out.width='2.0in'}

#set graphical parameters and colors
par(mar=c(5,4,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of DISABILITY RATING for GENERAL POPULATION
midpoints <- barplot(height=dout.gp,
                     space=0.5,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(10,12)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=dout.gp+8, y=midpoints, labels=paste(round(dout.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r dout.zscore`_

# Socioeconomic - Housing, Children, Internet

## Almost all Veterans live in independent housing units. They are also more likely than the General Population to live as married couples.
```{r gq_setup}

#Group Quarters VIETNAM VETERANS
gq.v <- svytotal(~TYPE, viet_gq_design)
#Housing Units VIETNAM VETERANS
hu.v <- svytotal(~TYPE, hou_viet_design)
#Combine GQ and Housing Unit for Vietnam VETERANS
type.v <- c(hu.v[1], gq.v[2:3])
#Extract Std. Errors
type.se.v <- c(SE(hu.v)[1], SE(gq.v)[2:3])
rm(gq.v, hu.v)

#Group Quarters GENERAL POPULATION
gq.gp <- svytotal(~TYPE, per55_gq_design)
#Housing Units GENERAL POPULATION
hu.gp <- svytotal(~TYPE, hou55_design)
#Combine GQ and Housing Unit for GENERAL POPULATION
type.gp <- c(hu.gp[1], gq.gp[2:3])
#Extract Std Errors
type.se.gp <- c(SE(hu.gp)[1], SE(gq.gp)[2:3])
rm(gq.gp, hu.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
type.z <- c() 
for(i in 1:length(type.v)){
  zscore<- (type.v[i]-type.gp[i])/sqrt(type.se.v[i]^2+type.se.gp[i]^2)
  type.z <- c(zscore, type.z)
  if(all(type.z > 1.96 | type.z < -1.96)==TRUE) type.zscore <- "Differences are significant at the 95% confidence level" else type.zscore <- "Differences are not significant."
}

#Convert to percentage
type.v <- type.v/sum(type.v)*100
type.gp <- type.gp/sum(type.gp)*100


```

```{r htype_setup}
#Household Type VIETNAM VETS,  extract std errors
htype.v <- svymean(~HouseType, hou_viet_design, na.rm=TRUE)
htype.se.v <- SE(htype.v)
#Household Type GENERAL POPULATION, extract std errors
htype.gp <- svymean(~HouseType, hou55_design, na.rm=TRUE)
htype.se.gp <- SE(htype.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
htype.z <- c() 
for(i in 1:length(htype.v)){
  zscore<- (htype.v[i]-htype.gp[i])/sqrt(htype.se.v[i]^2+htype.se.gp[i]^2)
  htype.z <- c(zscore, htype.z)
  if(all(htype.z > 1.96 | htype.z < -1.96)==TRUE) htype.zscore <- "Household Type differences are significant at the 95% confidence level" else htype.zscore <- "Household Type differences are not significant."
}
#multiply by 100 to get percentages
htype.v <- htype.v*100
htype.gp <- htype.gp*100

```
\columnsbegin
\column{.5\textwidth}
```{r gq_v_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,8,4,1), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of GROUP QUARTER for VIETNAM VETS
midpoints <- barplot(height=type.v,
                     space=0.5,
                     names.arg=c("Housing Unit", "Institutional\nGroup Quarters", "Non-institutional\nGroup Quarters"),
                     horiz=TRUE,
                     col=mycols[c(1,3)],
                     border=NA,
                     xlim=c(0,120),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=type.v+8, y=midpoints, labels=paste(round(type.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```

```{r gq_gp_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,8,4,1), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of GROUP QUARTER for GENERAL POPULATION
midpoints <- barplot(height=type.gp,
                     space=0.5,
                     names.arg=c("Housing Unit", "Institutional\nGroup Quarters", "Non-institutional\nGroup Quarters"),
                     horiz=TRUE,
                     col=mycols[c(2,4)],
                     border=NA,
                     xlim=c(0,120),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=type.gp+8, y=midpoints, labels=paste(round(type.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.4, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\newline
\tinyrfont
_`r type.zscore`_
\column{.5\textwidth}
```{r htype_v_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,8,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of HOUSEHOLD TYPE for VIETNAM VETS
midpoints <- barplot(height=htype.v,
                     names.arg=c("Family\nHH Female", "Family\nHH Male", "Married Couple", "Non-Family HH"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=htype.v+8, y=midpoints, labels=paste(round(htype.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r htype_gp_bar, out.width='1.75in'}

#set graphical parameters and colors
par(mar=c(5,8,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of HOUSEHOLD TYPE for VIETNAM VETS
midpoints <- barplot(height=htype.gp,
                     names.arg=c("Family\nHH Female", "Family\nHH Male",  "Married Couple", "Non Family HH"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=htype.gp+8, y=midpoints, labels=paste(round(htype.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\columnsend

<!-- setup for people-kids slide -->
```{r people_setup}
#Number of Persons in House VIETNAM VETS,  extract std errors
people.v <- svymean(~People, hou_viet_design, na.rm=TRUE)
people.se.v <- SE(people.v)
#Number of Persons in House GENERAL POPULATION, extract std errors
people.gp <- svymean(~People, hou55_design, na.rm=TRUE)
people.se.gp <- SE(people.gp)


#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
people.z <- c() 
for(i in 1:length(people.v)){
  zscore<- (people.v[i]-people.gp[i])/sqrt(people.se.v[i]^2+people.se.gp[i]^2)
  people.z <- c(zscore, people.z)
  if(all(people.z > 1.96 | people.z < -1.96)==TRUE) people.zscore <- "Differences are significant at the 95% confidence level" else people.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
people.v <- people.v*100
people.gp <- people.gp*100
```


```{r kids_setup}

#Presence of Children VIETNAM VETS
#Number of Persons in House VIETNAM VETS,  extract std errors
kids.v <- svymean(~Kids, hou_viet_design, na.rm=TRUE)
kids.se.v <- SE(kids.v)
#Number of Persons in House GENERAL POPULATION, extract std errors
kids.gp <- svymean(~Kids, hou55_design, na.rm=TRUE)
kids.se.gp <- SE(kids.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
kids.z <- c() 
for(i in 1:length(kids.v)){
  zscore<- (kids.v[i]-kids.gp[i])/sqrt(kids.se.v[i]^2+kids.se.gp[i]^2)
  kids.z <- c(zscore, kids.z)
  if(all(kids.z > 1.96 | kids.z < -1.96)==TRUE) kids.zscore <- "Differences are significant at the 95% confidence level" else kids.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
kids.v <- kids.v*100
kids.gp <- kids.gp*100

```

## Most households consist 1-2 people with no kids. Veteran households are `r round(people.v[2]-people.gp[2], digits = 0)`% more likely to have two people. This is probably due to their age, marital status and fewer widowers.

\columnsbegin
\column{.5\textwidth}

```{r people_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Number of People in House for VIETNAM VETS
midpoints <- barplot(height=people.v,
                     names.arg=c("1", "2", "3", "3+"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=people.v+8, y=midpoints, labels=paste(round(people.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)


```

```{r kids_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Number of KIDS in House for VIETNAM VETS
midpoints <- barplot(height=kids.v,
                     names.arg=c("Kids in HH", "No Kids"),
                     horiz=TRUE,
                     col=mycols[c(9, 11)],
                     border=NA,
                     xlim=c(0,115),
                     axes=TRUE,
                     xaxt="n",
                     las=0,
                     space =0.5
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=4, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=kids.v+8, y=midpoints, labels=paste(round(kids.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)


```
\column{.5\textwidth}
```{r people_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Number of People in House for GENERAL POPULATION
midpoints <- barplot(height=people.gp,
                     names.arg=c("1", "2", "3", "3+"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=people.gp+8, y=midpoints, labels=paste(round(people.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r kids_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Number of KIDS in House for General Population
midpoints <- barplot(height=kids.gp,
                     names.arg=c("Kids in HH", "No Kids"),
                     horiz=TRUE,
                     col=mycols[c(10, 12)],
                     border=NA,
                     xlim=c(0,115),
                     axes=TRUE,
                     xaxt="n",
                     las=0,
                     space=0.5
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=4, las=0, cex=1.5)
#custom labels 
text(x=kids.gp+8, y=midpoints, labels=paste(round(kids.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)


```
\columnsend
\tinyrfont
_`r kids.zscore`_

## Given the age group most households have the presence of someone 65 years and older while a small percentage also have the presence of someone 18 years and younger.

```{r elder_setup}

#Presence of 65 and over (Elder) VIETNAM VETS,  extract std errors
elder.v <- svymean(~Elder, hou_viet_design, na.rm=TRUE)
elder.se.v <- SE(elder.v)
#Presence of 65 and over (Elder) GENERAL POPULATION, extract std errors
elder.gp <- svymean(~Elder, hou55_design, na.rm=TRUE)
elder.se.gp <- SE(elder.gp)


#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
elder.z <- c() 
for(i in 1:length(elder.v)){
  zscore<- (elder.v[i]-elder.gp[i])/sqrt(elder.se.v[i]^2+elder.se.gp[i]^2)
  elder.z <- c(zscore, elder.z)
  if(all(elder.z > 1.96 | elder.z < -1.96)==TRUE) elder.zscore <- "Differences are significant at the 95% confidence level" else elder.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
elder.v <- elder.v*100
elder.gp <- elder.gp*100

```

```{r teen_setup}

#Presence of 18 and under (Teen)VIETNAM VETS,  extract std errors
teen.v <- svymean(~Teen, hou_viet_design, na.rm=TRUE)
teen.se.v <- SE(teen.v)
#Presence of 18 and under (Teen) GENERAL POPULATION, extract std errors
teen.gp <- svymean(~Teen, hou55_design, na.rm=TRUE)
teen.se.gp <- SE(teen.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
teen.z <- c() 
for(i in 1:length(teen.v)){
  zscore<- (teen.v[i]-teen.gp[i])/sqrt(teen.se.v[i]^2+teen.se.gp[i]^2)
  teen.z <- c(zscore, teen.z)
  if(all(teen.z > 1.96 | teen.z < -1.96)==TRUE) teen.zscore <- "Differences are significant at the 95% confidence level" else teen.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
teen.v <- teen.v*100
teen.gp <- teen.gp*100

```

\columnsbegin
\column{.5\textwidth}

```{r elder_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Presence of 65 and over for VIETNAM VETS
midpoints <- barplot(height=elder.v,
                     names.arg=c("1", "2+", "No Elder"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=elder.v+8, y=midpoints, labels=paste(round(elder.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r teen_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Presence of 65 and over for VIETNAM VETS
midpoints <- barplot(height=teen.v,
                     names.arg=c("1+ Teen", "No Teen"),
                     horiz=TRUE,
                     col=mycols[c(7,9)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.5
)


#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=4, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=teen.v+8, y=midpoints, labels=paste(round(teen.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

\column{.5\textwidth}

```{r elder_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Presence of 65 and over for GENERAL POPULATION
midpoints <- barplot(height=elder.gp,
                     names.arg=c("1", "2+", "No Elder"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=elder.gp+8, y=midpoints, labels=paste(round(elder.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r teen_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Presence of 65 and over for GENERAL POPULATION
midpoints <- barplot(height=teen.gp,
                     names.arg=c("1+ Teen", "No Teen"),
                     horiz=TRUE,
                     col=mycols[c(8, 10)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2, 
                     space=0.5
)


#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=4, las=0, cex=1.5)
#custom labels 
text(x=teen.gp+8, y=midpoints, labels=paste(round(teen.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

\columnsend
\tinyrfont
_`r elder.zscore`_

<!-- setup for vehicles/autos -->
```{r autos_setup}

#Presence of 18 and under (Teen)VIETNAM VETS,  extract std errors
autos.v <- svymean(~Autos, hou_viet_design, na.rm=TRUE)
autos.se.v <- SE(autos.v)
#Presence of 18 and under (Teen) GENERAL POPULATION, extract std errors
autos.gp <- svymean(~Autos, hou55_design, na.rm=TRUE)
autos.se.gp <- SE(autos.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
autos.z <- c() 
for(i in 1:length(autos.v)){
  zscore<- (autos.v[i]-autos.gp[i])/sqrt(autos.se.v[i]^2+autos.se.gp[i]^2)
  autos.z <- c(zscore, autos.z)
  if(all(autos.z > 1.96 | autos.z < -1.96)==TRUE) autos.zscore <- "Differences are significant at the 95% confidence level" else autos.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
autos.v <- autos.v*100
autos.gp <- autos.gp*100

```

## 90% or more households have at least one vehicle while Veteran households are `r round(autos.v[3]-autos.gp[3], digits = 0)`% more likely to have two vehicles. 

\columnsbegin
\column{0.5\textwidth}

```{r autos_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of No. of VEHICLES VIETNAM VETS
midpoints <- barplot(height=autos.v,
                     names.arg=c("0", "1", "2", "3+"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=autos.v+8, y=midpoints, labels=paste(round(autos.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

\column{0.5\textwidth}

```{r autos_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of No. of VEHICLES GENERAL POPULATION
midpoints <- barplot(height=autos.gp,
                     names.arg=c("0", "1", "2", "3+"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=autos.gp+8, y=midpoints, labels=paste(round(autos.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```

\columnsend
\tinyrfont
_`r autos.zscore`_

## Three-quarters of all households have internet access more than 50% don't have mobile broadband access. 

```{r internet_setup}

#Access to the Internet (ACCESS - Internet) VIETNAM VETS,  extract std errors
internet.v <- svymean(~Internet, hou_viet_design, na.rm=TRUE)
internet.se.v <- SE(internet.v)
#Access to the Internet (ACCESS - Internet) GENERAL POPULATION, extract std errors
internet.gp <- svymean(~Internet, hou55_design, na.rm=TRUE)
internet.se.gp <- SE(internet.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
internet.z <- c() 
for(i in 1:length(internet.v)){
  zscore<- (internet.v[i]-internet.gp[i])/sqrt(internet.se.v[i]^2+internet.se.gp[i]^2)
  internet.z <- c(zscore, internet.z)
  if(all(internet.z > 1.96 | internet.z < -1.96)==TRUE) internet.zscore <- "Differences are significant at the 95% confidence level" else internet.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
internet.v <- internet.v*100
internet.gp <- internet.gp*100

```

```{r mobilebb_setup}

#Broadband - Mobile Broadband Plan - MobileBB VIETNAM VETS,  extract std errors
mobile.v <- svymean(~MobileBB, hou_viet_design, na.rm=TRUE)
mobile.se.v <- SE(mobile.v)
#Broadband - Mobile Broadband Plan - MobileBB GENERAL POPULATION, extract std errors
mobile.gp <- svymean(~MobileBB, hou55_design, na.rm=TRUE)
mobile.se.gp <- SE(mobile.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
mobile.z <- c() 
for(i in 1:length(mobile.v)){
  zscore<- (mobile.v[i]-mobile.gp[i])/sqrt(mobile.se.v[i]^2+mobile.se.gp[i]^2)
  mobile.z <- c(zscore, mobile.z)
  if(all(mobile.z > 1.96 | mobile.z < -1.96)==TRUE) mobile.zscore <- "Differences are significant at the 95% confidence level" else mobile.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
mobile.v <- mobile.v*100
mobile.gp <- mobile.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r internet_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Access to the Internet VIETNAM VETS
midpoints <- barplot(height=internet.v,
                     names.arg=c("No","Yes"),
                     horiz=TRUE,
                     col=mycols[c(1,3)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.5
)

#custom labels 
text(x=internet.v+8, y=midpoints, labels=paste(round(internet.v, digits=1), "%"),  col="gray30")

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=4, las=0, cex=1.5, col="gray60")

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#Y-axis label
mtext("Internet Access", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#reset graph parameters
par(opar)

```

```{r mobilebb_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Mobile Broadband Plan VIETNAM VETS
midpoints <- barplot(height=mobile.v,
                     names.arg=c("No","Yes"),
                     horiz=TRUE,
                     col=mycols[c(5,7)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.5
)

#custom labels 
text(x=mobile.v+8, y=midpoints, labels=paste(round(mobile.v, digits=1), "%"),  col="gray30")

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=4, las=0, cex=1.5, col="gray60")

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#Y-axis label
mtext("Mobile Broadband Access", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#reset graph parameters
par(opar)

```

\column{0.5\textwidth}
```{r internet_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Access to the Internet GENERAL POPULATION
midpoints <- barplot(height=internet.gp,
                     names.arg=c("No", "Yes"),
                     horiz=TRUE,
                     col=mycols[c(2,4)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.5
)

#custom labels 
text(x=internet.gp+8, y=midpoints, labels=paste(round(internet.gp, digits=1), "%"),  col="gray30")

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=4, las=0, cex=1.5)

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#Y-axis label
mtext("Internet Access", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#reset grpaph parameters
par(opar)

```

```{r mobilebb_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Mobile Broadband Plan GENERAL POPULATION
midpoints <- barplot(height=mobile.gp,
                     names.arg=c("No","Yes"),
                     horiz=TRUE,
                     col=mycols[c(6,8)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.5
)

#custom labels 
text(x=mobile.gp+8, y=midpoints, labels=paste(round(mobile.gp, digits=1), "%"),  col="gray30")

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=4, las=0, cex=1.5)

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#Y-axis label
mtext("Mobile Broadband Access", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#reset grpaph parameters
par(opar)

```

\columnsend
\tinyrfont
_`r internet.zscore`_

# Socioeconomic - Education, Employment, and Income

## The differences for the education attainment levels are not statistically significant. 

```{r education_setup}

#Education Level - Educ VIETNAM VETS,  extract std errors
educ.v <- svymean(~Educ, viet_design, na.rm=TRUE)
educ.se.v <- SE(educ.v)
#Education Level - Educ GENERAL POPULATION, extract std errors
educ.gp <- svymean(~Educ, per55_design, na.rm=TRUE)
educ.se.gp <- SE(educ.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
educ.z <- c() 
for(i in 1:length(educ.v)){
  zscore<- (educ.v[i]-educ.gp[i])/sqrt(educ.se.v[i]^2+educ.se.gp[i]^2)
  educ.z <- c(zscore, educ.z)
  if(all(educ.z > 1.96 | educ.z < -1.96)==TRUE) educ.zscore <- "Differences are significant at the 95% confidence level" else educ.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
educ.v <- educ.v*100
educ.gp <- educ.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r educ_v_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Education Level VIETNAM VETS
midpoints <- barplot(height=educ.v,
                     names.arg=c("Advanced","Bachelor's","Graduate","Less than\nHigh School", "Some College"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7,9)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=educ.v+8, y=midpoints, labels=paste(round(educ.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{0.5\textwidth}
```{r educ_gp_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Education Level GENERAL POPULATION
midpoints <- barplot(height=educ.gp,
                     names.arg=c("Advanced","Bachelor's","Graduate","Less than\nHigh School", "Some College"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8,10)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=educ.gp+8, y=midpoints, labels=paste(round(educ.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r educ.zscore`_

## Non-Veterans are about 10% more likely to be in the labor force. Of those (Vietnam Veterans and non-Veterans) in the labor force, more than two-thirds are occupied in the private sector.

```{r emp_setup}

#Employment Status Recode - EmpPct VIETNAM VETS,  extract std errors
emp.v <- svymean(~EmpPct, viet_design, na.rm=TRUE)
emp.se.v <- SE(emp.v)
#Employment Status Recode - EmpPct GENERAL POPULATION, extract std errors
emp.gp <- svymean(~EmpPct, per55_design, na.rm=TRUE)
emp.se.gp <- SE(emp.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
emp.z <- c() 
for(i in 1:length(emp.v)){
  zscore<- (emp.v[i]-emp.gp[i])/sqrt(emp.se.v[i]^2+emp.se.gp[i]^2)
  emp.z <- c(zscore, emp.z)
  if(all(emp.z > 1.96 | emp.z < -1.96)==TRUE) emp.zscore <- "Differences are significant at the 95% confidence level" else emp.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
emp.v <- emp.v*100
emp.gp <- emp.gp*100

```

```{r worker_setup}

#Class of Worker - cowr VIETNAM VETS,  extract std errors
cowr.v <- svymean(~CowR, viet_design, na.rm=TRUE)
cowr.se.v <- SE(cowr.v)
#Class of Worker - cowr GENERAL POPULATION, extract std errors
cowr.gp <- svymean(~CowR, per55_design, na.rm=TRUE)
cowr.se.gp <- SE(cowr.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
cowr.z <- c() 
for(i in 1:length(cowr.v)){
  zscore<- (cowr.v[i]-cowr.gp[i])/sqrt(cowr.se.v[i]^2+cowr.se.gp[i]^2)
  cowr.z <- c(zscore, cowr.z)
  if(all(cowr.z > 1.96 | cowr.z < -1.96)==TRUE) cowr.zscore <- "Differences are significant at the 95% confidence level" else cowr.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
cowr.v <- cowr.v*100
cowr.gp <- cowr.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r emp_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Employment Status Recode VIETNAM VETS
midpoints <- barplot(height=emp.v,
                     names.arg=c("Employed", "Not in\nLabor Force", "Unemployed"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=emp.v+8, y=midpoints, labels=paste(round(emp.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r cowr_v_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Class of Worker VIETNAM VETS
midpoints <- barplot(height=cowr.v,
                     names.arg=c("Government","Private","Self-Employed", "Unemployed"),
                     horiz=TRUE,
                     col=mycols[c(5,7,9,11)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=cowr.v+8, y=midpoints, labels=paste(round(cowr.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{0.5\textwidth}
```{r emp_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Employment Status Recode GENERAL POPULATION
midpoints <- barplot(height=emp.gp,
                     names.arg=c("Employed", "Not in\nLabor Force", "Unemployed"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=emp.gp+8, y=midpoints, labels=paste(round(emp.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```

```{r cowr_gp_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Class of Worker GENERAL POPULATION
midpoints <- barplot(height=cowr.gp,
                     names.arg=c("Government","Private","Self-Employed", "Unemployed"),
                     horiz=TRUE,
                     col=mycols[c(6,8,10,12)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=cowr.gp+8, y=midpoints, labels=paste(round(cowr.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r emp.zscore`_

## While most Veterans and non-Veterans are well above the poverty, Veterans are about 5% less likely to be living in poverty.

```{r pov_setup}

#Income-to-Poverty RatioVIETNAM VETS,  extract std errors
pov.v <- svymean(~Pov, viet_design, na.rm=TRUE)
pov.se.v <- SE(pov.v)
#Income-to-Poverty Ratio GENERAL POPULATION, extract std errors
pov.gp <- svymean(~Pov, per55_design, na.rm=TRUE)
pov.se.gp <- SE(pov.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
pov.z <- c() 
for(i in 1:length(pov.v)){
  zscore<- (pov.v[i]-pov.gp[i])/sqrt(pov.se.v[i]^2+pov.se.gp[i]^2)
  pov.z <- c(zscore, pov.z)
  if(all(pov.z > 1.96 | pov.z < -1.96)==TRUE) pov.zscore <- "Differences are significant at the 95% confidence level" else pov.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
pov.v <- pov.v*100
pov.gp <- pov.gp*100

```

```{r povty_setup}

#Income-to-Poverty Rollup VIETNAM VETS,  extract std errors
povty.v <- svymean(~Povty, viet_design, na.rm=TRUE)
povty.se.v <- SE(povty.v)
#Income-to-Poverty Rollup GENERAL POPULATION, extract std errors
povty.gp <- svymean(~Povty, per55_design, na.rm=TRUE)
povty.se.gp <- SE(povty.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
povty.z <- c() 
for(i in 1:length(povty.v)){
  zscore<- (povty.v[i]-povty.gp[i])/sqrt(povty.se.v[i]^2+povty.se.gp[i]^2)
  povty.z <- c(zscore, povty.z)
  if(all(povty.z > 1.96 | povty.z < -1.96)==TRUE) povty.zscore <- "Differences are significant at the 95% confidence level" else povty.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
povty.v <- povty.v*100
povty.gp <- povty.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r pov_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Income-to-Poverty Ratio VIETNAM VETS
midpoints <- barplot(height=pov.v,
                     names.arg=c("0-99%", "100-149%", "150-199%", "200-299%","300-399%", "400%+"),
                     horiz=TRUE,
                     col=c("grey", mycols[c(1,3,5,7,9)]),
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=pov.v+8, y=midpoints, labels=paste(round(pov.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\newline
\tinyrfont
_`r pov.zscore`_

```{r povty_v_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Poverty Roll-up VIETNAM VETS
midpoints <- barplot(height=povty.v,
                     names.arg=c("At or\nAbove Poverty", "In Poverty"),
                     horiz=TRUE,
                     col=mycols[c(3,1)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=povty.v+8, y=midpoints, labels=paste(round(povty.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{0.5\textwidth}
```{r pov_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Income-to-Poverty Ratio GENERAL POPULATION
midpoints <- barplot(height=pov.gp,
                     names.arg=c("0-99%", "100-149%", "150-199%", "200-299%","300-399%", "400%+"),
                     horiz=TRUE,
                     col=c("grey", mycols[c(2,4,6,8,10)]),
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=pov.gp+8, y=midpoints, labels=paste(round(pov.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```

```{r povty_gp_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Poverty Roll-up GENERAL POPULATION
midpoints <- barplot(height=povty.gp,
                     names.arg=c("At or\nAbove Poverty", "In Poverty"),
                     horiz=TRUE,
                     col=mycols[c(4,2)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=povty.gp+8, y=midpoints, labels=paste(round(povty.gp, digits=1), "%"), col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r povty.zscore`_

## No major differences in Earnings. Though in terms of Income Veterans are more likely to be in brackets above $20K.

```{r pernpc_setup}

#Personal EarningsVIETNAM VETS,  extract std errors
pernpc.v <- svymean(~Pernpc, viet_design, na.rm=TRUE)
pernpc.se.v <- SE(pernpc.v)
#Personal Earnings GENERAL POPULATION, extract std errors
pernpc.gp <- svymean(~Pernpc, per55_design, na.rm=TRUE)
pernpc.se.gp <- SE(pernpc.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
pernpc.z <- c() 
for(i in 1:length(pernpc.v)){
  zscore<- (pernpc.v[i]-pernpc.gp[i])/sqrt(pernpc.se.v[i]^2+pernpc.se.gp[i]^2)
  pernpc.z <- c(zscore, pernpc.z)
  if(all(pernpc.z > 1.96 | pernpc.z < -1.96)==TRUE) pernpc.zscore <- "Differences are significant at the 95% confidence level" else pernpc.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
pernpc.v <- pernpc.v*100
pernpc.gp <- pernpc.gp*100

```

```{r pincpc_setup}

#Personal Income VIETNAM VETS,  extract std errors
pincpc.v <- svymean(~Pincpc, viet_design, na.rm=TRUE)
pincpc.se.v <- SE(pincpc.v)
#Personal Income GENERAL POPULATION, extract std errors
pincpc.gp <- svymean(~Pincpc, per55_design, na.rm=TRUE)
pincpc.se.gp <- SE(pincpc.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
pincpc.z <- c() 
for(i in 1:length(pincpc.v)){
  zscore<- (pincpc.v[i]-pincpc.gp[i])/sqrt(pincpc.se.v[i]^2+pincpc.se.gp[i]^2)
  pincpc.z <- c(zscore, pincpc.z)
  if(all(pincpc.z > 1.96 | pincpc.z < -1.96)==TRUE) pincpc.zscore <- "Differences are significant at the 95% confidence level" else pincpc.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
pincpc.v <- pincpc.v*100
pincpc.gp <- pincpc.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r pernpc_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Personal Earnings  VIETNAM VETS
midpoints <- barplot(height=pernpc.v,
                     names.arg=c("0-20", "20-39", "40-59", "60-79", "80-99", "100+"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7,9,11)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)
#custom labels 
text(x=pernpc.v+8, y=midpoints, labels=paste(round(pernpc.v, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("Earnings in 000s", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r pincpc_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Personal Income VIETNAM VETS
midpoints <- barplot(height=pincpc.v,
                     names.arg=c("0-20", "20-39", "40-59", "60-79", "80-99", "100+"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7,9,11)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#custom labels 
text(x=pincpc.v+8, y=midpoints, labels=paste(round(pincpc.v, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("Income in 000s", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0., col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

\column{0.5\textwidth}
```{r pernpc_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Personal Earnings  GENERAL POPULATION
midpoints <- barplot(height=pernpc.gp,
                     names.arg=c("0-20", "20-39", "40-59", "60-79", "80-99", "100+"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8,10,12)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     
                     las=2
)

#custom labels 
text(x=pernpc.gp+8, y=midpoints, labels=paste(round(pernpc.gp, digits=1), "%"), col="gray30")

#Y-axis label
mtext("Earnings in 000s", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```

```{r pincpc_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Personal Income GENERAL POPULATION
midpoints <- barplot(height=pincpc.gp,
                     names.arg=c("0-20", "20-39", "40-59", "60-79", "80-99", "100+"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8,10,12)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     
                     las=2
)

#Y-axis label
mtext("Income in 000s", side=2, adj=0.5, line=4, las=0, cex=1.5, col="gray60")

#custom labels 
text(x=pincpc.gp+8, y=midpoints, labels=paste(round(pincpc.gp, digits=1), "%"), col="gray30")

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```

\columnsend
\tinyrfont
_`r pincpc.zscore`_

## Of those recieving a retirement income, a majority of Veterans and non-Veterans get under $25K. Veteran are about 7% more likely to be in the 25K-50K income range. 

```{r retpc_setup}

#Retirement Income VIETNAM VETS,  extract std errors
retpc.v <- svymean(~Retpc, viet_design, na.rm=TRUE)
retpc.se.v <- SE(retpc.v)
#Retirement Income GENERAL POPULATION, extract std errors
retpc.gp <- svymean(~Retpc, per55_design, na.rm=TRUE)
retpc.se.gp <- SE(retpc.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
retpc.z <- c() 
for(i in 1:length(retpc.v)){
  zscore<- (retpc.v[i]-retpc.gp[i])/sqrt(retpc.se.v[i]^2+retpc.se.gp[i]^2)
  retpc.z <- c(zscore, retpc.z)
  if(all(retpc.z > 1.96 | retpc.z < -1.96)==TRUE) retpc.zscore <- "Differences are significant at the 95% confidence level" else retpc.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
retpc.v <- retpc.v*100
retpc.gp <- retpc.gp*100

```

\columnsbegin
\column{0.5\textwidth}

```{r retpc_v_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Personal Income VIETNAM VETS
midpoints <- barplot(height=retpc.v,
                     names.arg=c("0-25", "25-50", "50-75", "75-100", "100-125", "125+"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5,7,9,11)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#custom labels 
text(x=retpc.v+8, y=midpoints, labels=paste(round(retpc.v, digits=1), "%"),  col="gray30")

#Y-axis label
mtext("In 000s", side=2, adj=0.5, line=5, las=0, cex=1.5, col="gray60")

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

\column{0.5\textwidth}
```{r retpc_gp_bar}

#set graphical parameters and colors
par(mar=c(5,7,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Personal Income GENERAL POPULATION
midpoints <- barplot(height=retpc.gp,
                     names.arg=c("0-25", "25-50", "50-75", "75-100", "100-125", "125+"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6,8,10,12)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     
                     las=2
)

#custom labels 
text(x=retpc.gp+8, y=midpoints, labels=paste(round(retpc.gp, digits=1), "%"), col="gray30")

#Y-axis label
mtext("In 000s", side=2, adj=0.5, line=5, las=0, cex=1.5, col="gray60")

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)

#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset grpaph parameters
par(opar)

```
\columnsend
\tinyrfont
_`r retpc.zscore`_

## Overall Veterans and non-Veterans are not Food Stamp users, though Veterans are less likely to be users than the General Population. 

```{r fs_setup}

#Food Stamp VIETNAM VETS,  extract std errors
fs.v <- svymean(~FS, hou_viet_design, na.rm=TRUE)
fs.se.v <- SE(fs.v)
#Food Stamp GENERAL POPULATION, extract std errors
fs.gp <- svymean(~FS, hou55_design, na.rm=TRUE)
fs.se.gp <- SE(fs.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
fs.z <- c() 
for(i in 1:length(fs.v)){
  zscore<- (fs.v[i]-fs.gp[i])/sqrt(fs.se.v[i]^2+fs.se.gp[i]^2)
  fs.z <- c(zscore, fs.z)
  if(all(fs.z > 1.96 | fs.z < -1.96)==TRUE) fs.zscore <- "Differences are significant at the 95% confidence level" else fs.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
fs.v <- fs.v*100
fs.gp <- fs.gp*100

```

\columnsbegin
\column{0.5\textwidth}
```{r fs_v_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Food Stamp Use by VIETNAM VETS
midpoints <- barplot(height=fs.v,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(1,3)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=fs.v+8, y=midpoints, labels=paste(round(fs.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{0.5\textwidth}
```{r fs_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Food Stamp Use of GENERAL POPULATION
midpoints <- barplot(height=fs.gp,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(2,4)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=fs.gp+8, y=midpoints, labels=paste(round(fs.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```
\columnsend
\tinyrfont
_`r fs.zscore`_

# Socioeconomic - Health Insurance

## Nearly all Veterans and non-Veterans have health insurance coverage. Though Veterans tend to have less private and more public coverage. 

```{r hicov_setup}

#Health Insurance Coverage VIETNAM VETS,  extract std errors
hicov.v <- svymean(~HICOV, viet_design, na.rm=TRUE)
hicov.se.v <- SE(hicov.v)
#Health Insurance Coverage GENERAL POPULATION, extract std errors
hicov.gp <- svymean(~HICOV, per55_design, na.rm=TRUE)
hicov.se.gp <- SE(hicov.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
hicov.z <- c() 
for(i in 1:length(hicov.v)){
  zscore<- (hicov.v[i]-hicov.gp[i])/sqrt(hicov.se.v[i]^2+hicov.se.gp[i]^2)
  hicov.z <- c(zscore, hicov.z)
  if(all(hicov.z > 1.96 | hicov.z < -1.96)==TRUE) hicov.zscore <- "Differences are significant at the 95% confidence level" else hicov.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
hicov.v <- hicov.v*100
hicov.gp <- hicov.gp*100

```

```{r hitype_setup}

#Insurance Coverage Type VIETNAM VETS,  extract std errors
hitype.v <- svymean(~HITYPE, viet_design, na.rm=TRUE)
hitype.se.v <- SE(hitype.v)
#Insurance Coverage Type GENERAL POPULATION, extract std errors
hitype.gp <- svymean(~HITYPE, per55_design, na.rm=TRUE)
hitype.se.gp <- SE(hitype.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
hitype.z <- c() 
for(i in 1:length(hitype.v)){
  zscore<- (hitype.v[i]-hitype.gp[i])/sqrt(hitype.se.v[i]^2+hitype.se.gp[i]^2)
  hitype.z <- c(zscore, hitype.z)
  if(all(hitype.z > 1.96 | hitype.z < -1.96)==TRUE) hitype.zscore <- "Differences are significant at the 95% confidence level" else hitype.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
hitype.v <- hitype.v*100
hitype.gp <- hitype.gp*100


```

\columnsbegin
\column{0.5\textwidth}
```{r hicov_v_bar}

#set graphical parameters and colors
par(mar=c(5,5,4,1), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Health Insurance Coverage VIETNAM VETS
midpoints <- barplot(height=hicov.v,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(3,1)],
                     border=NA,
                     xlim=c(0,120),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=hicov.v+8, y=midpoints, labels=paste(round(hicov.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r hitype_v_bar}
#set graphical parameters and colors
par(mar=c(5,4,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Health Insurance Coverage Type VIETNAM VETS
midpoints <- barplot(height=hitype.v,
                     names.arg=c("Private", "Public &\nPrivate", "Public"),
                     horiz=TRUE,
                     col=mycols[c(1,3,5)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=hitype.v+8, y=midpoints, labels=paste(round(hitype.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```
\column{0.5\textwidth}
```{r hicov_gp_bar}

#set graphical parameters and colors
par(mar=c(5,5,4,1), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Health Insurance Coverage GENERAL POPULATION
midpoints <- barplot(height=hicov.gp,
                     names.arg=c("Yes", "No"),
                     horiz=TRUE,
                     col=mycols[c(4,2)],
                     border=NA,
                     xlim=c(0,120),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=hicov.gp+8, y=midpoints, labels=paste(round(hicov.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```

```{r hitype_gp_bar}

#set graphical parameters and colors
par(mar=c(5,4,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Health Insurance Coverage Type GENERAL POPULATION
midpoints <- barplot(height=hitype.gp,
                     names.arg=c("Private", "Public &\nPrivate", "Public"),
                     horiz=TRUE,
                     col=mycols[c(2,4,6)],
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=hitype.gp+8, y=midpoints, labels=paste(round(hitype.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```
\columnsend
\tinyrfont
_`r hitype.zscore`_

## Uses VA Care HINS6 / Specific Insurance - Ins

```{r vacare_setup}

#Uses VA Care HINS6 VIETNAM VETS,  extract std errors
vacare.v <- svymean(~HINS6, viet_design, na.rm=TRUE)
vacare.se.v <- SE(vacare.v)
#Uses VA Care HINS6 GENERAL POPULATION, extract std errors
vacare.gp <- svymean(~HINS6, per55_design, na.rm=TRUE)
vacare.se.gp <- SE(vacare.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
vacare.z <- c() 
for(i in 1:length(vacare.v)){
  zscore<- (vacare.v[i]-vacare.gp[i])/sqrt(vacare.se.v[i]^2+vacare.se.gp[i]^2)
  vacare.z <- c(zscore, vacare.z)
  if(all(vacare.z > 1.96 | vacare.z < -1.96)==TRUE) vacare.zscore <- "Differences are significant at the 95% confidence level" else vacare.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
vacare.v <- vacare.v*100
vacare.gp <- vacare.gp*100

```

```{r ins_setup}

#Specific Insurance - Ins VIETNAM VETS,  extract std errors
ins.v <- svymean(~Ins, viet_design, na.rm=TRUE)
ins.se.v <- SE(ins.v)
#Specific Insurance - Ins GENERAL POPULATION, extract std errors
ins.gp <- svymean(~Ins, per55_design, na.rm=TRUE)
ins.se.gp <- SE(ins.gp)

#significance test if z < -1.96 or Z>1,96, results are significant at the 95 confidence level
ins.z <- c() 
for(i in 1:length(ins.v)){
  zscore<- (ins.v[i]-ins.gp[i])/sqrt(ins.se.v[i]^2+ins.se.gp[i]^2)
  ins.z <- c(zscore, ins.z)
  if(all(ins.z > 1.96 | ins.z < -1.96)==TRUE) ins.zscore <- "Differences are significant at the 95% confidence level" else ins.zscore <- "Differences are not significant."
}
#multiply by 100 to get percentages
ins.v <- ins.v*100
ins.gp <- ins.gp*100

```

\columnsbegin
\column{0.5\textwidth}

```{r vacare_v_bar}
#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Uses VA Care HINS6 VIETNAM VETS
midpoints <- barplot(height=vacare.v,
                     names.arg=c("Uses VA", "Does Not\nUse VA"),
                     horiz=TRUE,
                     col=mycols[c(3,1)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.75
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=vacare.v+8, y=midpoints, labels=paste(round(vacare.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

```{r ins_v_bar, out.width='2.5in'}
#set graphical parameters and colors
par(mar=c(4,6,2,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Specific Insurance VIETNAM VETS
midpoints <- barplot(height=ins.v,
                     names.arg=c("Direct", "Employer &\nTricare", "Employer & VA", "IHS", "Medicaid", "Medicare", "Tricare", "VA & Private", "VA & Public", "VA Only", "VA & Public\n& Private"),
                     horiz=TRUE,
                     col=brewer.pal(n=11, "Set3"),
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     cex.names=0.6
)

#X-axis label
mtext("Percentage of Veterans", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=ins.v+8, y=midpoints, labels=paste(round(ins.v, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

\column{0.5\textwidth}

```{r vacare_gp_bar}

#set graphical parameters and colors
par(mar=c(5,6,4,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Uses VA Care HINS6 GENERAL POPULATION
midpoints <- barplot(height=vacare.gp,
                     names.arg=c("Uses VA", "Does Not\nUse VA"),
                     horiz=TRUE,
                     col=mycols[c(4,2)],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     space=0.75
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=vacare.gp+8, y=midpoints, labels=paste(round(vacare.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0.1, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```

```{r ins_gp_bar, out.width='2.5in'}

#set graphical parameters and colors
par(mar=c(4,6,2,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Specific Insurance GENERAL POPULATION
midpoints <- barplot(height=ins.gp,
                     names.arg=c("Direct", "Employer &\nTricare", "Employer & VA", "IHS", "Medicaid", "Medicare", "Tricare", "VA & Private", "VA & Public", "VA Only", "VA & Public\n& Private"),
                     horiz=TRUE,
                     col=mycols[1:11],
                     border=NA,
                     xlim=c(0,110),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     cex.names=0.6
)

#X-axis label
mtext("Percentage of General Population", col="gray60", side=1, adj=0.25, line=2.5, las=0, cex=1.5)
#custom labels 
text(x=ins.gp+8, y=midpoints, labels=paste(round(ins.gp, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)
```
\columnsend
\tinyrfont
_`r vacare.zscore`_


# Utilization of VA Benefits & Services

## Most Vietnam Era Veterans recieve heath care or compensation benefits. 

```{r util_v_bar}
#set graphical parameters and colors
par(mar=c(4,6,2,2), cex=1.75, col.lab="gray30", col.axis="gray60")

#barplot of Specific Insurance VIETNAM VETS
midpoints <- barplot(height=uvr15$Yes,
                     names.arg=c("Compensation\nor Pension", "Compensation Only", "Education", "Health Care", "Burial\nGrave Marker", "Home Loan", "Vocational\nRehab", "Compensation\nOr Health Care"),
                     horiz=TRUE,
                     col=brewer.pal(n=8, "Set3"),
                     border=NA,
                     xlim=c(0,100),
                     axes=TRUE,
                     xaxt="n",
                     las=2,
                     cex.names=0.6
)

#X-axis label
mtext("Percentage of Veteran Users", side=1, adj=0.25, line=2.5, las=0, cex=1.5, col="gray60")
#custom labels 
text(x=uvr15$Yes+8, y=midpoints, labels=paste(round(uvr15$Yes, digits=1), "%"),  col="gray30")
#custom x-axis
axis(side = 1, at = c(0,25,50,75,100), pos=0, col.ticks = "gray60",  cex.axis=0.75, lwd=0, lwd.ticks = 0.15)

#reset graph parameters
par(opar)

```

# Contact Information

## This profile was prepared by the [\textcolor{blue}{National Center for Veterans Analysis and Statistics}](https://www.va.gov/vetdata/)

For general inquiries, please email us at \textcolor{blue}{VANCVAS@va.gov}
